Antigenic phenotypes and phylogenetic metrics improve forecasts of seasonal influenza A/H3N2 evolution

### 2019-12-05 manuscript/main.tex
Update model results tables including test results
Removes approximation of future diversity from tables and text in favor of a
later summary of these statistics in the corresponding results sections. Also
adds the files for model test results on natural populations.

\begin{table*}[ht]
  \begin{center}
    \input{tables/simulated_model_selection.tex}
    \caption{
      Model coefficients and validation performance for simulated populations ordered from best to worst by distance to the future.
      Coefficients are the mean $\pm$ standard deviation for each metric in a given model across 33 training windows.
      Distance to the future measures the distance in amino acids between estimated and observed future populations.
      Approximation of the future diversity measures the difference between the average Hamming distance between the estimated and observed future populations and the future population's average Hamming distance to itself (i.e., the diversity of the future populations).
      Models with values that are closer to or less than zero produce better approximations of the future.
      The number of times (and percentage of total times) each model outperformed the naive model measures the benefit of each model over a model than estimates no change between current and future populations.
    }
    \label{table_simulated_model_selection}
  \end{center}
\end{table*}

@@

Both two-metric composite models performed better than their corresponding individual models (Table~\ref{table_natural_model_selection} and Fig.~\ref{fig:unadjusted_composite_model_accuracy_and_coefficients_for_natural_populations}).
Although the three-metric composite model performed slightly worse than the individual LBI model, this composite model outperformed the naive model the most of any model with 19 (83\%) times out of 23.
The composite of LBI and non-epitope mutations performed the best overall with an average distance to the future of 5.44 $\pm$ 1.80 AAs and an approximation of future diversity near zero (-0.02 $\pm$ 1.50 AAs).

>>>>

\begin{table*}[ht]
  \begin{center}
    \input{tables/simulated_model_selection.tex}
    \caption{
      Model coefficients and validation performance for simulated populations ordered from best to worst by distance to the future.
      Coefficients are the mean $\pm$ standard deviation for each metric in a given model across 33 training windows.
      Distance to the future measures the distance in amino acids between estimated and observed future populations.
      The number of times (and percentage of total times) each model outperformed the naive model measures the benefit of each model over a model than estimates no change between current and future populations.
    }
    \label{table_simulated_model_selection}
  \end{center}
\end{table*}

@@

Both two-metric composite models performed better than their corresponding individual models (Table~\ref{table_natural_model_selection} and Fig.~\ref{fig:unadjusted_composite_model_accuracy_and_coefficients_for_natural_populations}).
Although the three-metric composite model performed slightly worse than the individual LBI model, this composite model outperformed the naive model the most of any model with 19 (83\%) times out of 23.
The composite of LBI and non-epitope mutations performed the best overall with an average distance to the future of 5.44 $\pm$ 1.80 AAs.

### 2019-12-05 manuscript/supplement.tex
Update model results tables including test results
Removes approximation of future diversity from tables and text in favor of a
later summary of these statistics in the corresponding results sections. Also
adds the files for model test results on natural populations.

>>>>

\begin{table*}[ht]
  \begin{center}
    \input{tables/complete_natural_model_test.tex}
    \caption{
      All model coefficients and test performance for natural populations ordered from best to worst by distance to the future, as in Supplemental Table~\ref{table_simulated_model_test}.
      Results are based on 8 test timepoints.
    }
    \label{sup_table:complete_natural_model_test}
  \end{center}
\end{table*}
